Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-29 paper/paper.Rmd
another comment reply

>>>>

<!--- P: Because this is one method within the "buffering" category and so far my approach was to label these as "<method name> (<pkg>)".
Apparently this is suboptimal from your point of view - how can we do better?
Also the visual appearance of level 4 headings in the PDF is suboptimal - maybe we should do this someway different. -->
